Dispersion distance and the matter distribution of the Universe in dispersion space

### 2015-06-04 writeup/dm_space_distortions.tex
line of sight --> line-of-sight and reference 'standard ping' in conclusion

The $\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}$ term arises because the
misinterpretation of the radial distance causes the observed tracer density to
be compared to the wrong background density. The $\frac{2}{\chi}$ term is
caused by a misinterpretation of angular distances when the radial distance is
mis-measured.  In both cases analogous terms are in principle present in 
redshift space but are
negligible. Because radial velocities are only sourced by modes with large
radial wave vector, there is near perfect cancellation along the line of sight
and thus is very little net error in radial distance.

@@

However, the lack of a kernel simplifies tomography---the use of sources at
multiple redshifts to unmix spatial scales.
Lensing tomography is inexact because the kernel's shape depends on
the source redshift, thus re-weighting the line-of-sight integral.
In contrast, the integrand in the dispersion-space integral
term is completely independent of the limit of integration, meaning
contributions from different parts of the line of sight (and thus different
spatial scales) can be separated exactly. A detailed study of dispersion space
tomography is beyond the scope of this work.  To avoid our results being
sensitive to the hard-to-model small scales, we assume that the contribution to the
integral term from radial distances $\chi'' < 500\,{\rm Mpc}/h$ are well
measured by the correlations with these radial slices. We thus ignore
contributions to the integral term from below this distance and neglect the
information from these slices in our sensitivity measurements. The smallest
spatial scale that contributes to our plotted angular power spectra out to
$\ell=1000$ is thus $k=2\,h/{\rm Mpc}$.

@@

We have proposed using cosmological FRB sources as 3D tracers of the
large-scale structure,
using dispersion to estimate radial distance. It can be seen in
Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
electron density along the line of sight, inducing mis-estimates of radial
distance and thus apparent clustering. These dispersion-space distortions could
be used
to study the distribution of free electrons in the Universe on large-scales.
There have been other proposals to use FRBs in cosmology 
\citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}, however these
schemes have either not been three dimensional
or required externally measured redshifts
for the sources.

>>>>

The $\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}$ term arises because the
misinterpretation of the radial distance causes the observed tracer density to
be compared to the wrong background density. The $\frac{2}{\chi}$ term is
caused by a misinterpretation of angular distances when the radial distance is
mis-measured.  In both cases analogous terms are in principle present in 
redshift space but are
negligible. Because radial velocities are only sourced by modes with large
radial wave vector, there is near perfect cancellation along the line-of-sight
and thus is very little net error in radial distance.

@@

However, the lack of a kernel simplifies tomography---the use of sources at
multiple redshifts to unmix spatial scales.
Lensing tomography is inexact because the kernel's shape depends on
the source redshift, thus re-weighting the line-of-sight integral.
In contrast, the integrand in the dispersion-space integral
term is completely independent of the limit of integration, meaning
contributions from different parts of the line-of-sight (and thus different
spatial scales) can be separated exactly. A detailed study of dispersion space
tomography is beyond the scope of this work.  To avoid our results being
sensitive to the hard-to-model small scales, we assume that the contribution to the
integral term from radial distances $\chi'' < 500\,{\rm Mpc}/h$ are well
measured by the correlations with these radial slices. We thus ignore
contributions to the integral term from below this distance and neglect the
information from these slices in our sensitivity measurements. The smallest
spatial scale that contributes to our plotted angular power spectra out to
$\ell=1000$ is thus $k=2\,h/{\rm Mpc}$.

@@

We have proposed using cosmological FRB sources as standard pings to trace the 3D 
large-scale structure of the Universe using dispersion distance. It can be seen in
Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
electron density along the line-of-sight in each sky direction, inducing mis-estimates of radial
distance and thus apparent clustering. These dispersion-space distortions could
be used
to study the distribution of free electrons in the Universe on large-scales.
There have been other proposals to use FRBs in cosmology 
\citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}, however these
schemes have either not been three dimensional
or required externally measured redshifts
for the sources.
